calerror

### 2024-01-30 simCalibration.Rmd
new

results_all <- rbindlist(lapply(1:10, function(iter) {
  try({
    print(iter)
  results <- rbindlist(lapply(c(20, 30, 40, 50, 75, 100, 200, 300, 500), get_widths_cal) )
  results$iter <- iter
  })
  return(results)
}))

@@

ggplot(results  , aes(x = n, y = width, color = as.factor(alpha), linetype = Status)) + geom_line()  + scale_x_log10()

>>>>

results_all <- rbindlist(lapply(1:010, function(iter) {
  try({
    print(iter)
  results <- rbindlist(lapply(c(20, 30, 40, 50, 75, 100, 200, 300 ), get_widths_cal) )
  results$iter <- iter
  })
  return(results)
}))

@@

ggplot(results  , aes(x = n, y = width, color = as.factor(alpha), linetype = Status)) + geom_smooth(se=F)  + scale_x_log10()
